\documentclass[11pt,a4paper]{article}

\usepackage[margin=1in]{geometry}
\usepackage{longtable}
\usepackage{array}
\usepackage{hyperref}

\title{\textbf{Daily Work Log}}
\author{Gaurav Kumar \\
Shiv Narang}
\date{\today}

\begin{document}

\maketitle

\section*{Overview}
This document records daily progress and tasks completed during the project.

\vspace{0.5cm}

\section*{Work Log}

\begin{longtable}{|p{3cm}|p{12cm}|}
\hline
\textbf{Date} & \textbf{Work Done} \\
\hline
\endfirsthead

\hline
\textbf{Date} & \textbf{Work Done} \\
\hline
\endhead

% ---- Entries start here ----

Till Jan End &
Studied previous report and set up the project using Kotlin language for frontend and python for backend. We are using the Android Studio IDE. \\
\hline

First Week of Feb &
Created a basic clean UI and and integrated the backend. The feedback form currently captures user ratings and some device statistics \\
\hline

10 Feb 2026 &
Created the design document and worklog for the project. Tested on some incoming and outgoing call cases.  \\
\hline

12 Feb 2026 &
Researched on the problem of app getting killed by android and not being able to detect calls made after a long time. \\
\hline

13 Feb 2026 &
Decided to use app as a foreground process with a persistent notification indicating it is waiting for call. Implementing this feature. \\
\hline

14 Feb 2026 &
Completed implementation and testing of the foreground feature.\\
\hline

% ---- Add more entries as needed ----

\end{longtable}

\end{document}
